Summarize results on robustness of EM algorithm

### 2015-10-26 analysis/summarize_dsc_robust.Rmd
add index

Now check out the example that showed the biggest convergence problem
```{r}
#check out which one showed biggest convergence problem
prob = res[which.max(res$score.diff1),]
setwd("../output")
prob_eg = loadExample(dsc_robust,seed=prob$seed,scenario=as.character(prob$scenario),method=as.character(prob$method))
setwd("../analysis")
```

>>>>

Now check out the example that showed the biggest convergence problem
```{r}
#check out which one showed biggest convergence problem
prob = res[which.max(res$score.diff1),]
prob_eg = load_example(dsc_robust,seed=prob$seed,scenario=as.character(prob$scenario),method=as.character(prob$method),homedir="../output")
```
